%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{-25pt}}r}
      \textbf{\spaceskip=0.25em University of Hamburg - Security and Distributed Systems Research Group} & Hamburg, Germany \\
      \textit{\small Student Research Assistant} & \textit{\small June 2025 - Present, Part Time} \\
    \end{tabular*}\vspace{-7pt}
      \resumeItemListStart
        \resumeItem{\normalsize{Developing Python-based tools and applications for research data management and security analysis, implementing algorithms for distributed network systems.}}
        \resumeItem{\normalsize{Contributing to the NFDIxCS (National Research Data Infrastructure for Computer Science) project, collaborating on interdisciplinary projects involving AI and data science methodologies.}}
        \resumeItem{\normalsize{\textbf{Technical Skills:} Python Development, Research Methodology, Cybersecurity, Network Security, Distributed Systems, Docker, Git}}
      \resumeItemListEnd  

    \resumeSubheading
      {\spaceskip=0.25em University of Hamburg - Language Technology Research Group}{Hamburg, Germany} 
      {Project Student Assistant}{Feb 2025 - May 2025, Part Time}
      \resumeItemListStart
        \resumeItem{\normalsize{Contributed to the development of the DATS Project (Discourse Analysis Tool Suite), an advanced NLP platform for automated text analysis and discourse processing, implementing key features and functionality enhancements.}}
        \resumeItem{\normalsize{Developed and maintained full-stack components including React TypeScript frontend interfaces and FastAPI backend services, implementing RESTful APIs and database integrations for improved system performance and user experience.}}
        \resumeItem{\normalsize{Implemented NLP processing modules, text preprocessing pipelines, and data analysis algorithms, working with machine learning frameworks to handle large-scale linguistic datasets and generate meaningful insights.}}
        \resumeItem{\normalsize{\textbf{Technical Skills:} Natural Language Processing, Machine Learning, React TypeScript, FastAPI, Python, RESTful APIs, Database Integration, Docker, Git, Agile Development, Text Analytics, Data Processing}}
      \resumeItemListEnd  

    \resumeSubheading
      {\spaceskip=0.25em Adtech Media Solutions}{New Delhi, India} 
      {Data Analyst Intern}{Feb 2023 - Nov 2023}
      \resumeItemListStart
        \resumeItem {\normalsize{Conducted Market research, analyzed data to develop insights and marketing strategies and generated reports on key metrics for clients.}}
        \resumeItem {\normalsize{Created interactive dashboards and data visualizations to present complex analytical findings to clients and support data-driven decision making.}}
        \resumeItem {\normalsize{\textbf{Technical Skills:} Python, Pandas, Tableau, Jupyter, Github, Git}}
      \resumeItemListEnd  
      
    \resumeSubheading
      {\spaceskip=0.25em Maseehum Task Manager Private Limited (mTm)}{New Delhi, India}
      {Web Developer}{Apr 2023 - Oct 2023}
    \resumeItemListStart
      \resumeItem{\normalsize{Developed and designed the complete full-stack website for a fintech hardware distribution company specializing in biometric devices, POS terminals, and payment systems serving 500+ retailers nationwide.}}
      \resumeItem{\normalsize{Built responsive web interfaces showcasing product catalogs for electronic and fintech hardware including Mantra/Morpho biometric scanners, Android POS terminals, and thermal receipt printers.}}
      \resumeItem{\normalsize{\textbf{Technical Skills:} React TypeScript, Flask, Full-Stack Development, E-commerce Integration, Responsive Design, RESTful APIs, Git, GitHub}}
    \resumeItemListEnd

    \resumeSubheading
      {\spaceskip=0.25em National Informatics Center}{New Delhi, India}
      {Data Analyst Intern}{May 2022 - July 2022}
      \resumeItemListStart
        \resumeItem{\normalsize{Scraped data from Indian Govt. Services Portal, organized it into CSV files, performed visualizations, manipulations, etc.}}
        \resumeItem{\normalsize{\textbf{Technical Skills:} Python, Pandas, BeautifulSoup4, Seaborn, Matplotlib}}
      \resumeItemListEnd

 \resumeSubHeadingListEnd
    
