%-----------PROJECTS-----------
\section{Projects}
    \vspace{2pt}
    \resumeSubHeadingListStart
    
    \resumeProjectHeading
          {{\textbf{\large{{GitGood}}} \space
          \href{https://github.com/nnayz/GitGood}{\faGithub}} 
          $|$ { Python, GitHub API, OAuth, Machine Learning, Web Development}}{}
          \resumeItemListStart
            \resumeItem{\normalsize{Built a comprehensive web application that integrates with GitHub via OAuth to analyze and visualize repository data, commit history, and code differences.}}
            \resumeItem{\normalsize{Integrated AI-powered chat assistant using custom RAG system to answer contextual questions about code changes and repository evolution.}}
          \resumeItemListEnd 
          \vspace{2pt}
          
       \resumeProjectHeading
          {{\textbf{\large{{MyTorch}}} \space
          \href{https://github.com/nnayz/MyTorch}{\faGithub}} 
          $|$ { Python, NumPy, Deep Learning, Neural Networks}}{}
          \resumeItemListStart
            \resumeItem{\normalsize{Developed a minimal deep learning library inspired by PyTorch, implementing fundamental neural network operations using only NumPy as the Python library dependency, building everything from scratch with fully connected linear layers for educational and prototyping purposes.}}
            \resumeItem{\normalsize{Built core functionalities including forward and backward propagation, gradient computation, and optimization algorithms to facilitate understanding of deep learning fundamentals.}}
          \resumeItemListEnd 
           \vspace{2pt}
           
       \resumeProjectHeading
            {{\textbf{\large{{Taxibee}}} \space
            \href{https://github.com/Taxibeee/Taxibee}{\faGithub}} 
           $|$ { TypeScript, Material UI, React, Google Cloud, Docker, FastAPI, Apache Kafka, MySQL}}{}
           \resumeItemListStart
             \resumeItem{\normalsize{Engineered a real-time data management web application for taxi companies, featuring comprehensive dashboards for monitoring driver performance and operational metrics.}}
             \resumeItem{\normalsize{Implemented live streaming capabilities for order and transaction data processing, enabling real-time tracking of business operations and customer interactions.}}
             \resumeItem{\normalsize{Developed automated revenue calculation and driver payout management systems with live analytics to optimize financial operations and driver compensation.}}
           \resumeItemListEnd 
           \vspace{2pt}
           
       \resumeProjectHeading
            {{\textbf{\large{{Momentum (WIP)}}} \space
            \href{https://github.com/nnayz/Momentum}{\faGithub}} 
           $|$ { Web Scraping, Content Analysis, Research Tools, Machine Learning, Python}}{}
           \resumeItemListStart
             \resumeItem{\normalsize{Developing a research assistant web application inspired by Anara Labs' Anara, designed to streamline academic and technical research workflows.}}
             \resumeItem{\normalsize{Building automated web content extraction and organization systems to gather, process, and categorize research materials from multiple online sources.}}
             \resumeItem{\normalsize{Implementing intelligent summarization algorithms to condense and present research findings in structured, actionable formats for enhanced productivity.}}
           \resumeItemListEnd 
         
    \resumeSubHeadingListEnd
% \vspace{-12pt}